The Essence of Summarization\\ in Pushdown Flow Analyses\\ \textbf{Supplemental Material}

### 2014-02-21 content.tex
Drafted a why-we-matter section.

@@

%%
The first of these is a semantic approach to memoizing that is a straight-forward analog to the programmatic approach.
%
A memoizing program will call a function in a non-tail context in order to obtain the result, store the result to an ``enough context to obtain the same result'' key in a table (in a pure setting, just the function and arguments), and continue with the result.
%
The semantics we use is functionally equivalent, only we have a special stack frame that acts as the non-tail context that additionally stores results in a table that is part of the machine state.
%
In the case of a baseline abstract machine for AAM, a CESK machine~\citep{dvanhorn:Felleisen1987Calculus}, the store is relevant to the evaluation of functions.
%
As such, the CES portion of a state suffices as ``enough context.''
%
For a semantics that inspects the stack, ``enough context'' is CES plus the inspected portion of K.
%%

>>>>

\section{Models in higher-order analysis}

Constructing models and analyzing models are different processes.
%
The goal of this work is to simplify the program $\to$ model process.
%
First-order languages have the luxury of a fully-precise control flow graph that can be extracted from a program AST in linear time.
%
In a sense, the first-order world gets their models ``for free.''
%
Higher-order recursion schemes (HORS) are a powerful model for simply typed functional programs with good model-checking properties~\citep{dvanhorn:Ong2006ModelChecking}, but the program $\to$ HORS process is narrowly applicable.
%
It is still a matter of mystery for HORS to support programming language features like mutable state and untyped computation.
%%
As a middle ground, we show a simple way to transform one's programming language semantics into a what can be viewed as a pushdown model constructor.
%%

%%
When striving for precision, the interconnectedness of data-flow and control-flow analysis in higher-order languages extend upwards to the interconnectedness of model construction and model-checking.
%
When we tune the abstractions, the result of translating semantics can range from control-flow analysis~\citep{dvanhorn:VanHorn2010Abstracting} to a symbolic execution engine~\citep{dvanhorn:TobinHochstadt2012Higherorder}.
%
These are all forward-executing techniques, so the analogy does not fully extend to all analytical technologies.
%
We find the power and simplicity in the constructions enticing nonetheless.
%
The resulting artifacts can be used as models in the first-order tools~\citep{ianjohnson:bandera}

@@

%%
The first of these is a semantic approach to memoizing that is a straight-forward analog to the programmatic approach.
%
A memoizing program will call a function in a non-tail context in order to obtain the result, store the result to an \emph{enough context to obtain the same result} key in a table (in a pure setting, just the function and arguments), and continue with the result.
%
The semantics we use is functionally equivalent, only we have a special stack frame that acts as the non-tail context that additionally stores results in a table that is part of the machine state.
%
In the case of a baseline abstract machine for AAM, a CESK machine~\citep{dvanhorn:Felleisen1987Calculus}, the store is relevant to the evaluation of functions.
%
As such, the CES portion of a state suffices as ``enough context.''
%
For a semantics that inspects the stack, ``enough context'' is CES plus the inspected portion of K.
%%
